lfl: Linguistic Fuzzy Logic in \R{} -- Part I

### 2021-02-06 article1.tex
Updates from Overleaf

\Martin{Utekly mi obrazky pod reference na konec clanku - nevim proc. \\ Premyslim nad tim delenim clanku na part I a Part II. Mozna pri zkraceni tech prikladu se to vejde do jednoho clanku. Porad totiz tapu, kde tu delici mezeru udelat a jak se v te druhe casti neopakovat. }

@@

\begin{figure}[tbp]
	\centering
	\includegraphics[scale=0.3]{DEE.png}
	\caption{Visual sketch of fuzzy sets representing some particular evaluative linguistic expressions. Specific defuzzification DEE is charted too.}\label{fig_dee}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=0.8]{figure/horizon-1.pdf}
    \caption{Horizons for the atomic expressions \emph{small}, \emph{medium} and \emph{big} in the unilateral trichotomy (\code{ctx3(0, 0.5, 1)})}
    \label{fig:horizon}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.59]{figure/lingexpr1-1.pdf}
    \\
    \includegraphics[scale=0.59]{figure/lingexpr2-1.pdf}
    \\
    \includegraphics[scale=0.59]{figure/lingexpr3-1.pdf}
    \caption{All pre-defined linguistic expressions for the unilateral trichotomy context \code{ctx3}}
    \label{fig:lingexpr}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics[scale=0.80]{figure/triangular1-1.pdf}
        \caption{\code{triangular(0, 0.5, 1)}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics[scale=0.80]{figure/triangular2-1.pdf}
        \caption{\code{triangular(-Inf, 0.5, 1)}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics[scale=0.80]{figure/raisedcos1-1.pdf}
        \caption{\code{raisedcosinal(0, 0.5, 1)}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics[scale=0.80]{figure/raisedcos2-1.pdf}
        \caption{\code{raisedcosinal(0, 0.5, Inf)}}
    \end{subfigure}
    \caption{Triangular and raised-cosinal functions}
    \label{fig:triangular}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \newsavebox{\largestimage}
    \savebox{\largestimage}{\includegraphics[width=0.4\textwidth]{figure/fcut_plot1-1.pdf}}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \usebox{\largestimage}
        \caption{\code{merge=1}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \raisebox{\dimexpr0.07\ht\largestimage}{%
            \includegraphics[width=0.82\textwidth]{figure/fcut_plot2-1.pdf}}
        \caption{\code{merge=2}}
    \end{subfigure}
    \caption{Results of the \code{fcut} call with \code{breaks=c(1, 3, 5, 7, 9)} and different settings of \code{merge}.}
    \label{fig:fcut}
\end{figure}

@@

Internally, the rule base produced by the \code{searchrules()} function is an instance of the \code{farules} class. It is a list of two elements, \code{rules} and \code{statistics}, where \code{rules} is a list of character vectors of rule predicate names. The first element of these vectors is a consequent of the rule, the rest is the antecedent. The \code{statistics} element is a matrix that assigns some quality measures to each rule:
%
\input{chunks/chunk-searchrules2}
%
The \code{as.data.frame()} function converts the \code{farules} object to a usual data frame:
%
\input{chunks/chunk-searchrules3}
%
The \code{antecedent()} or \code{consequent()} functions create a list of antecedents or consequents from the \code{farules} object:
%
\input{chunks/chunk-searchrules4}

>>>>

@@

\begin{figure}[ht]
	\centering
	\includegraphics[scale=0.3]{DEE.png}
	\caption{Visual sketch of fuzzy sets representing some particular evaluative linguistic expressions. Specific defuzzification DEE is charted too.}\label{fig_dee}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.8]{figure/horizon-1.pdf}
    \caption{Horizons for the atomic expressions \emph{small}, \emph{medium} and \emph{big} in the unilateral trichotomy (\code{ctx3(0, 0.5, 1)})}
    \label{fig:horizon}
\end{figure}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[scale=0.59]{figure/lingexpr1-1.pdf}
    \\
    \includegraphics[scale=0.59]{figure/lingexpr2-1.pdf}
    \\
    \includegraphics[scale=0.59]{figure/lingexpr3-1.pdf}
    \caption{All pre-defined linguistic expressions for the unilateral trichotomy context \code{ctx3}}
    \label{fig:lingexpr}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics[scale=0.79]{figure/triangular1-1.pdf}
        \caption{\code{triangular(0, 0.5, 1)}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics[scale=0.79]{figure/triangular2-1.pdf}
        \caption{\code{triangular(-Inf, 0.5, 1)}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics[scale=0.79]{figure/raisedcos1-1.pdf}
        \caption{\code{raisedcosinal(0, 0.5, 1)}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics[scale=0.79]{figure/raisedcos2-1.pdf}
        \caption{\code{raisedcosinal(0, 0.5, Inf)}}
    \end{subfigure}
    \caption{Triangular and raised-cosinal functions}
    \label{fig:triangular}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \newsavebox{\largestimage}
    \savebox{\largestimage}{\includegraphics[width=0.4\textwidth]{figure/fcut_plot1-1.pdf}}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \usebox{\largestimage}
        \caption{\code{merge=1}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \raisebox{\dimexpr0.07\ht\largestimage}{%
            \includegraphics[width=0.82\textwidth]{figure/fcut_plot2-1.pdf}}
        \caption{\code{merge=2}}
    \end{subfigure}
    \caption{Results of the \code{fcut} call with \code{breaks=c(1, 3, 5, 7, 9)} and different settings of \code{merge}.}
    \label{fig:fcut}
\end{figure}

@@

Internally, the rule base produced by the \code{searchrules()} function is an instance of the \code{farules} class. It is a list of two elements, \code{rules} and \code{statistics}, where \code{rules} is a list of character vectors of rule predicate names. The first element of these vectors is a consequent of the rule, the rest is the antecedent. The \code{statistics} element is a matrix that assigns some quality measures to each rule. The \code{as.data.frame()} function converts the \code{farules} object to a usual data frame:
%
\input{chunks/chunk-searchrules3}
%
The \code{antecedent()} or \code{consequent()} functions create a list of antecedents or consequents from the \code{farules} object.
%
%\input{chunks/chunk-searchrules4}
